Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\underline{\em Example 4.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type1:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2}$, $H$ $=$ $\set{h_1,$ $h_2,$ $..., h_6}$, and $V = \set{v_1, v_2, ..., v_5}$. The set $\J_1$ contains the following tuples: $(\alpha, \beta_2, h_2, v_3)$, $(\alpha, \beta_2, h_2, v_5)$, $(\alpha, \beta_2, h_5, v_3)$, and $(\alpha,$ $\beta_2, h_5, v_6)$. \done

@@

As mentioned before, for a result tuple $(r_1, ..., r_{k-2}, h, v)$ of this type, a rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of $h$ or $v$ or both. As (i) there are $k-2$ choices for $i$ and (ii) $h$ and $v$ together have four endpoints, we can divide Type 2 further into $4(k-2)$ ``sub-types'': in subtype 1 (resp., 2), $r_1$ covers the left (resp., right) endpoint of $h$, in subtype 3 (resp., 4), $r_1$ covers the bottom (resp., top) endpoint of $v$, in subtype 5 (resp., 6), $r_2$ covers the left (resp., right) endpoint of $h$, etc. It is possible for the result tuple to belong to multiple sub-types simultaneously. Next, we will focus on producing the result tuples of a particular sub-type:
\myeqn{
    \J_2  &=& \{(r_1, ..., r_{k-2}, h, v) \in \J(R1, ..., R_{k-2}, H, V) \mid \text{$r_{k-2}$ covers} \nn \\[-0.5mm]
    && \text{the left endpoint of $h$}\}. \label{eqn:hv:type2:J2}
}
The other sub-types can be found analogously.

>>>>

\extraspacing {\underline{\em Example 4.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type1:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$ (the solid rectangle), $R_2 = \set{\beta_2, \beta_2}$ (the dashed rectangles), $H$ $=$ $\set{h_1,$ $h_2,$ $..., h_6}$, and $V = \set{v_1, v_2, ..., v_5}$. The set $\J_1$ contains the following tuples: $(\alpha, \beta_2, h_2, v_3)$, $(\alpha, \beta_2, h_2, v_5)$, $(\alpha, \beta_2, h_5, v_3)$, and $(\alpha,$ $\beta_2, h_5, v_6)$. \done

@@

As mentioned before, for a result tuple $(r_1, ..., r_{k-2}, h, v)$ of this type, a rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of $h$ or $v$ or both. As (i) there are $k-2$ choices for $i$ and (ii) $h$ and $v$ together have four endpoints, we can divide Type 2 further into $4(k-2)$ ``sub-types'': in subtype 1 (resp., 2), $r_1$ covers the left (resp., right) endpoint of $h$, in subtype 3 (resp., 4), $r_1$ covers the bottom (resp., top) endpoint of $v$, in subtype 5 (resp., 6), $r_2$ covers the left (resp., right) endpoint of $h$, etc. It is possible for the result tuple to belong to multiple sub-types simultaneously. Next, we will focus on producing the result tuples of a particular sub-type:
\myeqn{
    \J_2  &=& \{(r_1, ..., r_{k-2}, h, v) \in \J(R1, ..., R_{k-2}, H, V) \mid \text{$r_{k-2}$ covers the left endpoint of $h$}\}. \label{eqn:hv:type2:J2}
}
The other sub-types can be found analogously.
